### 2021-02-23 text/draft.tex
metrics

In this chapter I will construct three distinct gold standards in order
to assess the quality of machine indexing the sample data set with
Annif.\\
!! Say something about assessments of Annif that have already been
carried out.

@@

@@

!! Discussion of metrics

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Golub.2016}{}%
Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
Automatic Indexing or Classification in the Context of Retrieval.''}
\emph{Journal of the Association for Information Science and Technology}
67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.

@@

>>>>

In this chapter I will construct two distinct gold standards in order to
assess the quality of machine indexing the sample data set with Annif.\\
!! Say something about assessments of Annif that have already been
carried out.

@@

In this chapter I will assess the quality of the sample data set's
indexing with Annif based on the native and foreign gold standards.

@@

The metrics used for the assessment are precision, recall and F1 score.
Precision and recall are standard metrics for indexing quality (e.g.,
Gantert 2016, 197) whereby the F1 score plays are more prominent role in
the assessment of machine indexing (e.g., Suominen 2018, 11--14; Toepfer
and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
(such as indexing consistency, transparency, reproducability) that are
neglected here.

Let us briefly look at the definitions and motivations of the chosen
metrics. Recall that a suggestion of a subject term is correct if and
only if the subject term is in the native gold standard. The possible
outcomes are summarized in Table 1.

\begin{table}[h]
\centering
\begin{tabular}{lllll}
 &                       & \multicolumn{2}{l}{Suggested by Annif?}            &  \\ \cline{3-4}
 & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{Yes} &  \\ \cline{2-4}
\multicolumn{1}{l|}{\multirow{2}{*}{In gold standard?}} & \multicolumn{1}{l|}{No}  & \multicolumn{1}{l|}{True negative}  & \multicolumn{1}{l|}{False positive} &  \\ \cline{2-4}
\multicolumn{1}{l|}{}                                   & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{False negative} & \multicolumn{1}{l|}{True positive}  &  \\ \cline{2-4}
\end{tabular}
\caption{Annif confusion matrix.}
\label{tab:confusion-matrix}
\end{table}

\hypertarget{precision}{%
\paragraph{Precision}\label{precision}}

``Precision'' is the fraction of the correctly suggested subject terms;
a suggestion is correct if and only if it is in the native gold
standard:

\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{True positive} + \text{False positive}}\)

Or put as question: what fraction of the subject terms suggested by
Annif are also in the native gold standard?

\hypertarget{recall}{%
\paragraph{Recall}\label{recall}}

``Recall'' is the fraction of correct subject terms out of all correct
subject terms:

\(\text{Precision} = \displaystyle \frac{\text{True positive}}{\text{False negative} + \text{False positive}}\)

Put as question: what fraction of the subject terms in the gold standard
were suggested by Annif?

\hypertarget{f1-score}{%
\paragraph{F1-score}\label{f1-score}}

The F1-score is the harmonic mean between precision and recall:

\(\text{F1} = \displaystyle 2 * \frac{\text{Precision} * \text{Recall}}{\text{Precision} + \text{Recall}}\)

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Gantert.2016}{}%
Gantert, Klaus. 2016. \emph{Bibliothekarisches Grundwissen}. 9.,
vollst{ä}ndig neu bearbeitete und erweiterte Auflage. Berlin: {De
Gruyter Saur}. \url{https://doi.org/10.1515/9783110321500}.

\leavevmode\hypertarget{ref-Golub.2016}{}%
Golub, Koraljka, Dagobert Soergel, George Buchanan, Douglas Tudhope,
Marianne Lykke, and Debra Hiom. 2016. {``A Framework for Evaluating
Automatic Indexing or Classification in the Context of Retrieval.''}
\emph{Journal of the Association for Information Science and Technology}
67 (1): 3--16. \url{https://doi.org/10.1002/asi.23600}.

@@

\leavevmode\hypertarget{ref-Suominen.2018}{}%
Suominen, Osma. 2018. {``Annif: DIY Automated Subject Indexing Using
Multiple Algorithms.''} \emph{LIBER Quarterly} 29 (1): 1--25.
\url{https://doi.org/10.18352/lq.10285}.

\leavevmode\hypertarget{ref-Toepfer.2016}{}%
Toepfer, Martin, and Andreas Oskar Kempf. 2016. {``Automatische
Indexierung Auf Basis von Titeln Und Autoren-Keywords -- Ein
Werkstattbericht.''} \emph{027.7 Zeitschrift f{ü}r Bibliothekskultur /
Journal for Library Culture} 4 (2): 84--97.
\url{https://0277.ch/ojs/index.php/cdrs_0277/article/view/156/354}.
